### 2019-03-01 sections/intuition.tex
Various fixes in intuition section

This section gives an overview over the core concepts of task-oriented programming.

@@

The following program shows the different collaboration operators in the setting of making a breakfast.
Users have a choice ($\Xor$) whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel ($\And$).
When drink and food are prepared, users can step ($\Next$) to eating the results.

@@

There are three ways in which tasks are modular.
First, larger tasks are composed from smaller ones.
Second, tasks are first-class, they can be arguments and results of functions.
Third, tasks can be values of other tasks.
These aspects make it possible for programmers to model custom collaboration patterns.

@@

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneous to each such event.

@@

The sole purpose of editors is to interact with users by remembering the last value that has been sent to them.
There are no output events.
As values of editors can be observed, for example by a user interface, editors serve as facilities for both input and output.
An empty editor ($\Enter$) stands for a prompt to input data,
while a filled editor ($\Edit$) can be seen either as outputting a value, or as an input that comes with a default value.

@@

\TOPHAT allows a simple solution to this problem, using guarded steps.
Steps can be guarded with arbitrary expressions.
The parallel combinator can be used to watch two shared editors at the same time.
Let \TS{match}, \TS{paper}, and \TS{tobacco} be references to Booleans.
The smokers are defined as follows.
% The problem is then specified as follows.
\begin{TASK}
  let continue = \<<x,y>>. if x /\ y then smoke else fail in
  let tobaccoSmoker = (update match <&> update paper) >>? continue in
  let paperSmoker = (update tobacco <&> update match) >>? continue in
  let matchSmoker = (update tobacco <&> update paper) >>? continue
\end{TASK}
When the agent supplies two of the ingredients by setting the respective shares to \TS{True}, only the step of the smoker that waits for those becomes enabled.

>>>>

This section gives an overview of the core concepts of task-oriented programming.

@@

The following program shows the different collaboration operators in the setting of making breakfast.
Users have a choice ($\Xor$) whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel ($\And$).
When both the drink and the food are prepared, users can step ($\Next$) to eating the result.

@@

There are three ways in which tasks are modular.
First, larger tasks are composed of smaller ones.
Second, tasks are first-class, they can be arguments and results of functions.
Third, tasks can be values of other tasks.
These aspects make it possible for programmers to model custom collaboration patterns.

@@

Input events drive evaluation of tasks.
When the system receives a valid event, it applies this event to the current task, which results in a new task.
In this way the system communicates with the environment.
Inputs are synchronous.
We assume systems react instantaneously to each if those events.

@@

The sole purpose of editors is to interact with users by remembering the last value that has been sent to them.
There are no output events.
As values of editors can be observed, for example by a user interface, editors facilitate both input and output.
An empty editor ($\Enter$) stands for a prompt to input data,
while a filled editor ($\Edit$) can be seen either as outputting a value, or as an input that comes with a default value.

@@

\TOPHAT allows a simple solution to this problem, using guarded steps.
Steps can be guarded with arbitrary expressions.
The parallel combinator can be used to watch two shared editors at the same time.
Let \TS{match}, \TS{paper}, and \TS{tobacco} be references to Booleans.
The smokers are defined as follows.
% The problem is then specified as follows.
\begin{TASK}
  let continue = \<<x,y>>. if x /\ y then smoke else fail in
  let tobaccoSmoker = (update match <&> update paper) >>? continue in
  let paperSmoker = (update tobacco <&> update match) >>? continue in
  let matchSmoker = (update tobacco <&> update paper) >>? continue in
  tobaccoSmoker <&> paperSmoker <&> matchSmoker
\end{TASK}
When the agent supplies two of the ingredients by setting the respective shares to \TS{True}, only the step of the smoker that waits for those becomes enabled.
